Test

### 2016-07-22 Berkeley_PD_Stop.Rmd
072216

# Split information about the individual from other information
stop_df <- stop_df %>%
  mutate(Other = str_replace_all(Dispositions, "[ ,]{0,2}[a-zA-Z0-9]{6}", "")) %>%
  mutate(Other = str_replace_all(Other, "^[ ,]{0,4}", "")) %>%
  mutate(Other = str_replace(Other, ",$", ""))

@@

stop_df <- melt(stop_df, id = c("Incident.Number", "Call.Date.Time", "Location", "Incident.Type", "Other")) %>%
  arrange(Incident.Number)

@@

dispositions <- separate(stop_df, Dispositions, into = c("Individual_1", "Individual_2", "Individual_3", "Individual_4", "Individual_5", "Individual_6"), extra = "merge", fill = "right")

>>>>

# Split other information from information about the individual(s)
stop_df <- stop_df %>%
  mutate(Other = str_replace_all(Dispositions, "[ ,]{0,2}[a-zA-Z0-9]{6}", "")) %>%
  mutate(Other = str_replace_all(Other, "^[ ,]{0,4}", "")) %>%
  mutate(Other = str_replace(Other, ",$", ""))

@@

stop_df <- melt(stop_df, id = c("Incident.Number", "Call.Date.Time", "Location", "Incident.Type", "Other")) %>%
  na.omit() %>%
  arrange(Incident.Number)

@@

dispositions <- separate(stop_df, Dispositions, into = c("Individual_1", "Individual_2", "Individual_3", "Individual_4", "Individual_5"), extra = "merge", fill = "right")
